\documentclass{cmc}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=red,
}
\urlstyle{same}

\begin{document}
\maketitle
\pagestyle{fancy}
\tableofcontents
\lhead{\textit{\textbf{Computational Motor Control, Spring 2020} \\
    Python exercise, Lab 0, NOT GRADED}} \rhead{Student \\ Names}

\newpage
\section*{Student names: \ldots (please update)}

\textit{Instructions: This document contains the instructions to
  install and get familiarized with Python programming.  \textbf{This
    lab is not graded}. This file does not need to be submitted and is
  provided for your own benefit.}

\newpage
\section{Introduction to Python}

\subsection{Basic Python Concepts}

In this section we will quickly go over the list of topics given
below.  You can open and run the individual files marked with the same
topic name using Spyder.  We suggest you to go through each section
individually and spend time exploring each of the concepts by making
changes to the code and observing the outputs.

\begin{enumerate}
  \setcounter{enumi}{-1}
\item HelloWorld
\item Imports
\item Data Types
\item Math
\item Conditional Statements
\item Data Containers : Lists, Tuples and Dictionaries
\item Functions
\item Loops
\item Numpy
\item Matplotlib
\item Classes
\end{enumerate}

While you are executing each of the small exercises, try to learn how
to use different features of Spyder. Especially the help and debugging
feature.  When you are unsure of any command, use the help service
either the one built into Python or Spyder.  After familiarizing
yourself with the above concepts try to solve the following python
exercises.

\newpage
\subsection{Exercise 1}
\textbf{Check if the following matrix M is a magic square or not?}

\textit{\textbf{Hint : } A magic square is a square matrix which
  contains distinct integers and whose sum along any of its individual
  rows or columns or diagonal is a constant.  The constant is called
  as a magic constant or magic sum or magic square}

\begin{equation*}
  \label{eq:1}
  M =
  \begin{bmatrix}
    16 & 3  & 2  & 13 \\
    5  & 10 & 11 & 8  \\
    9  & 6  & 7  & 12 \\
    4 & 15 & 14 & 1
  \end{bmatrix}
\end{equation*}

\textit{\textbf{Further Step : } Try if you can generalize your script
  to have a function to check any arbitrary matrix if it is a magic
  square or not.  Import the function as a module in another script
  and use it to check the matrix M}

\subsection{Exercise 2 - Plotting a function}

\textit{Plot the following function $f(x)$ over an interval [0, 2]
  with proper labels and title}

\begin{equation*}
  \label{eq:3}
  f(x) = sin(x - 2)e^{-x^2}
\end{equation*}

\newpage
\section{References and additional useful links}
\label{sec:references}

\subsection{Python}
\label{sec:python_ref}
\begin{itemize}
\item
  \href{http://mathesaurus.sourceforge.net/matlab-numpy.html}{NumPy
    for MATLAB users}
\item \href{https://python.swaroopch.com}{A byte of python}
\item \href{http://nbviewer.jupyter.org/gist/rpmuller/5920182}{A Crash
    Course in Python for Scientists}
\item The official \href{https://docs.python.org/2/}{Python
    documentation} should be your first stop when looking for
  information
\item \href{http://numpy.scipy.org/}{numpy}
\item \href{http://www.scipy.org/}{scipy}
\item \href{http://matplotlib.sourceforge.net/}{matplotlib}
\end{itemize}

\subsection{Git}
\label{sec:git_ref}
\begin{itemize}
\item \href{https://try.github.io/levels/1/challenges/1}{Try Git!}
\item
  \href{https://marklodato.github.io/visual-git-guide/index-en.html}{A
    Visual Git Reference}
\end{itemize}

\subsection{Spyder}
\label{sec:spyder_ref}
\begin{itemize}
\item
  \href{http://www.southampton.ac.uk/~fangohr/blog/spyder-the-python-ide.html#first-steps-with-spyder}{Getting started with Spyder}
\end{itemize}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

%  LocalWords:  iTerm